---
title: "Peer-graded Assignment week 3"
author: "Fabio Alexandre Alberini Lopes Lima"
date: "10 de diciembre de 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#setwd("Documents/DataScientist/9dataProduct/paw3/")
```

```{r get_data, message=FALSE}
library(xlsx)
library(plotly)
library(stringi)

filenames <- c("nomnac16.xlsx","nomnac15.xlsx","nomnac14.xlsx","nomnac13.xls","nomnac12.xls", "nomnac11.xls","nomnac10.xls")
years <- 2016:2010
Bnames <- character()
Gnames <- character()

Snames <- data.frame(name = character(), count=numeric(), rank= numeric(), sex = factor(), year = numeric())

for (i in 1:7) {
    boys  <- read.xlsx(filenames[i], sheetIndex = 2, startRow = 5, endRow = 105, header = F, stringsAsFactors = F, colIndex = c(1:2))
    girls <- read.xlsx(filenames[i], sheetIndex = 2, startRow = 5, endRow = 105, header = F, stringsAsFactors = F, colIndex = c(4:5))
    
    boys[,3] <- 1:nrow(boys); boys[,4] <- "M"; boys[,5] <- years[i]; names(boys) <- names(Snames)
    girls[,3] <- 1:nrow(girls); girls[,4] <- "M"; girls[,5] <- years[i]; names(girls) <- names(Snames)
    
    Snames <- rbind(Snames, boys, girls)
    Bnames <- c(Bnames, boys[1:6,1])
    Gnames <- c(Gnames, girls[1:6,1])
}
Bnames <- unique(stri_trim(Bnames))
Gnames <- unique(stri_trim(Gnames))
Snames[,1] <- stri_trim(Snames[,1])

```

## Most popular names for babies in Spain since 2010.

### About the Data

You can find all the source data and code in the git hub repository <https://github.com/faall/ProgrammingAssignment9_3> 

Data was obtained from Spain's National Statistics Institute <http://www.ine.es/dyngs/INEbase/es/operacion.htm?c=Estadistica_C&cid=1254736177009&menu=resultados&secc=1254736195498&idp=1254734710990>

I have taken the top 6 names for each year and then constructed the graphic with all the names in the top list. The idea is to compare the evolution of popular names in this decade.

## Common Names for Girls

```{r plot_girls}
plot_ly(Snames[Snames$name %in% Gnames,],
        x=~year,
        y=~rank,
        color = ~name, 
        type = "scatter",
        mode = "lines") %>%
      layout(xaxis = list(title ="Year"),
             yaxis = list(title ="Rank", autorange = "reversed", rangemode = "tozero"))
```

## Common Names for Boys

```{r plot_boys}
plot_ly(Snames[Snames$name %in% Bnames,],
        x=~year,
        y=~rank,
        color = ~name, 
        type = "scatter",
        mode = "lines") %>%
      layout(xaxis = list(title ="Year"),
             yaxis = list(title ="Rank", autorange = "reversed", rangemode = "tozero"))
```
